Viscous Transport in Eroding Porous Media

### 2019-08-21 docs/transport/erosion_transport.tex
do result section in transport paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 Bodies at a Low Porosity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider a second example with 20 eroding bodies, but with a smaller
initial porosity.  In Figure~\ref{fig:ErodingLow20vort}, we plot the
eroding geometry and porosity at four evenly spaced instances in time.
Again, the color is the vorticity in the bulk whose magnitude is
equivalent to the erosion rate.  Each body is discretized with $N_\iin =
256$, and the smallest distance between two bodies at the initial
condition is ???\todo[inline]{SH: Fill in this number}.  At this
resolution, this corresponds to a spacing of ???$h$ which is much
too small for the trapezoid rule.  By applying the Barycentric
quadrature rule, there is no issue simulating the erosion until all the
bodies have eroded.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 Bodies at a Low Porosity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider a second example with 20 eroding bodies, but with a smaller
initial porosity.  In Figure~\ref{fig:ErodingLow20vort}, we plot the
eroding geometry and porosity at four evenly spaced instances in time.
Again, the color is the vorticity in the bulk whose magnitude is
equivalent to the erosion rate.  Each body is discretized with $N_\iin =
256$, and the smallest distance between two bodies at the initial
condition is 0.0216\todo[inline]{SH: Fill in this number}.  At this
resolution, this corresponds to a spacing of $3.0814h$ which is much
too small for the trapezoid rule.  By applying the Barycentric
quadrature rule, there is no issue simulating the erosion until all the
bodies have eroded.
